Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Address review 2B point 1, about TCP Vegas

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
%\todo{expand, and discuss how this evolution has occurred to date}
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency. It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.
\todo{Review B: Alternatives might have deployment challenges (e.g.,
fairness between delay and loss based algorithms).}

>>>>

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency, although it is known to be less
aggressive than standard TCP, and is prone to starvation; FAST TCP 
\cite{jin:2004:fast-tcp} is a more modern delay-based algorithm that 
competes well with standard TCP in many environments, and is seeing 
commercial deployment. 
It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.
The development of TCP congestion control shows that there might be
fairness issues as new algorithms are deployed, but the network does not
prevent the deployment of those algorithms.
